---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `clusteringRF`

<!-- badges: start -->
[![R-CMD-check](https://github.com/sistm/clusteringRF/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/sistm/clusteringRF/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

`clusteringRF` performs Random Forests of Divisive Monothetic ([`divclust`](https://github.com/chavent/divclust)) Trees for Unsupervised Clustering.

## Installation

You can install the development version of clusteringRF from [GitHub](https://github.com/). 

`clusteringRF`depends on a custopmized implementation of the [`divclust`](https://github.com/chavent/divclust) package, that must first be installed with the following:

```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("sistm/divclust")
```

Then, `clusteringRF` can be installed with:
```{r, eval=FALSE}
remotes::install_github("sistm/clusteringRF")
```

## Example

```{r}
library(clusteringRF)
library(palmerpenguins)
mypeng <- as.data.frame(penguins)
mypeng$year <- factor(as.character(mypeng$year),
                         levels=c("2007", "2008", "2009"),
                         ordered=TRUE)

forest_clust <- clusteringRF(na.omit(mypeng[mypeng$sex=="male", -c(1, 7)]), ntrees = 50, ncores = 1)

resume <- summary(forest_clust)
plot(resume)
```



